Summer 2025 ToDo

### 2025-11-13 Relations/Paper/Definitions.tex
Minor edits

\begin{definition}
    An abstract rewrite system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where
     $A$ is a set and $R_\alpha$ is a set of binary relations on $A$.
\end{definition}

>>>>

\begin{definition}
    \ule{An abstract rewrite system({ARS})} is a structure $\mathcal{A} = (A, R_\alpha)$ where
     $A$ is a set and $R_\alpha$ is a set of binary relations on $A$.
\end{definition}

### 2025-11-13 Relations/Paper/Introduction.tex
New definition layout. Typos fixed. Proper URLs
Minor edits

We present a formalization of the basic Abstract Rewriting Systems (ARS) theory as presented in Term Rewriting Systems [TeReSe]
 \cite{Terese}, using the Agda proof assistant.
This work is part of a larger effort to develop a library of formalized programming language theory (PL)
at Appalachian State University.
Since Term Rewriting Systems (TRS) play a foundational role in programming languages,
while ARS encompass the basic facts about rewriting relations in general,
establishing these facts is part of the necessary infrastructure required to
pursue the broader project.  The present contribution can therefore be seen as
``bootstrapping'' Appstate's new formalized PL repository.

@@

Recall that a relation is strongly normalizing iff its converse is well-founded. \cite[Def.1.1.13]{Terese}.
Since normalization is a central concept in ARS theory,
we pay special attention to the concept of well-foundedness.
The standard constructive definition does not even allow one to show that SN implies WN,
as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
We therefore looked at a number of variations of this notion in the constructive context,
their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.

>>>>

We present a formalization of the basic Abstract Rewriting Systems (ARS) theory as presented in Term Rewriting Systems [TeReSe]
 \cite{Terese}, using the Agda proof assistant.
This work is part of a larger effort to develop a library of formalized programming language theory (PL)
at Appalachian State University.
Since Term Rewriting Systems (TRS) play a foundational role in programming languages,
while ARS encompass the basic facts about rewriting relations in general,
establishing these facts is part of the necessary infrastructure required to
pursue the broader project.  The present contribution can therefore be seen as
``bootstrapping'' Appalachian State's new formalized PL repository.

@@

Recall that a relation is strongly normalizing iff its converse is well-founded. \cite[Def.1.1.13]{Terese}.
Since normalization is a central concept in ARS theory,
we pay special attention to the concept of well-foundedness.
The standard constructive definition does not even allow one to show that SN implies WN,
as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda} \sacomment{Should this now be ARS/Examples.agda?}.
We therefore looked at a number of variations of this notion in the constructive context,
their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
